Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-30 CJM/second letter to CJM.tex
Edits to the second letter to CJM

\begin{document}
{\hfill {2017 May 11} \\ 
%\rightline{Calgary}
}

@@

In addition to making changes prompted by the referee's comments, we have corrected an error pointed out to us in an e-mail from Will Savin.  Namely, we assumed incorrectly at the beginning of section 3 that any character on $G(k)$ would vanish on $G\der(k)$.  Every character vanishes on $G(k)\der$, but in general these two groups are not the same (for example, if $G = \SL_2$ over $\FFF$ or $\PGL_2$ over a finite field of odd characteristic).  We adjusted the exposition in the introduction and beginning of section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12 and Theorem 5.2.  We also added Section 4, where we describe some approaches for geometrizing characters that do not vanish on $G\der(k)$.

We now describe the changes made to address the referee's remarks.

\begin{enumerate}[label=(\arabic*)]
\item We have added Section 3.2.3 on Rigidification to address this problem, and restructured the discussion around what was Lemma 3.3.
\item The new section also addresses this concern.  Note that the reviewer is correct that $n^*_2(\mu)$ agrees with $p^*_2(\mu)$, though we did not add this fact explicitly to the paper, because it was not needed in the discussion of rigidification.
\end{enumerate}

@@

@@

Best  regards,
\bigskip

>>>>

\begin{document}
{\hfill {2017 August 30} \\ 
%\rightline{Calgary}
}

@@

Our thanks again to the referee for corrections and very helpful remarks, to which we now respond.

\begin{enumerate}[label=(\arabic*)]
\item We have added Section 3.2.3 on Rigidification to address this problem, and restructured the discussion around what was Lemma 3.3.
\item Section 3.2.3 also addresses this concern.  Note that the reviewer is correct that $n^*_2(\mu)$ agrees with $p^*_2(\mu)$, though we did not add this fact explicitly to the paper, because it was not needed in the discussion of rigidification.
\end{enumerate}

@@

In addition to making changes prompted by the referee's comments, we have corrected an error pointed out to us in an e-mail from Will Savin.  Namely, we assumed incorrectly at the beginning of Section 3 that any character on $G(k)$ would vanish on $G\der(k)$.  Every character vanishes on $G(k)\der$, but in general these two groups are not the same (for example, if $G = \SL_2$ over $\FFF$ or $\PGL_2$ over a finite field of odd characteristic).  We adjusted the exposition in the introduction and beginning of Section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12 and Theorem 5.2.  We also added Section 4, where we describe some approaches for geometrizing characters that do not vanish on $G\der(k)$.

@@

Best  regards,
\vskip1.5cm
